Dependent Object Types

### 2012-08-06 article.tex
a bit more details on subst lemma

The substitution lemma states that if (1) $v_2 \in \relv {k_2}
{\Gamma_{12}} {s_{12}} {T_2}$ and (2) $t \in \rele {k_1} {\Gamma_1
  \envplus{{x_i} : S}} {s_1} T$ and (3) $\Gamma \ts {T_2} \sub S$ with
$\Gamma$ included in $\Gamma_1$ and $\Gamma_{12}$ included in
$\Gamma_1$ and $s_{12}$ included in $s_1$, then $\subst {v_2} {x_i}
{t_i} \in \rele {\min(k_1,k_2)} {\Gamma_{12}} {s_{12}} T$.

\begin{proofsketch}
By (1) and (3), it should hold that (4) $v_2 \in \relv {k_2}
{\Gamma_{12}} {s_{12}} {S}$. Since (2) holds, it should also hold that
${t_i} \in \rele {\min(k_1,k_2)} {\Gamma_{12} \envplus{{x_i} : S}}
{s_{12}} T$ by monotonicity of the logical relation on all
subscripts. Then, we can instantiate $x_i$ in the complete store to
map to what $v_2$ maps to. This should be fine by (4) and
monotonicity. Thus, ${t_i} \in \rele {\min(k_1,k_2)} {\Gamma_{12}
  \envplus{{x_i} : S}} {s_{12} \envplus{{x_i} \mapsto s_{12}(v)}}
T$. This implies what needs to be shown.
\end{proofsketch}

>>>>

The substitution lemma states that if (1) $v_2 \in \relv {k_2}
{\Gamma_{12}} {s_{12}} {T_2}$ and (2) $t \in \rele {k_1} {\Gamma_1
  \envplus{{x_i} : S}} {s_1} T$ and (3) $\Gamma \ts {T_2} \sub S$ with
(4) $x_i \not\in \fn(T)$ and $\Gamma$ included in $\Gamma_1$ and
$\Gamma_{12}$ included in $\Gamma_1$ and $s_{12}$ included in $s_1$,
then $\subst {v_2} {x_i} {t_i} \in \rele {\min(k_1,k_2)} {\Gamma_{12}}
{s_{12}} T$.

\begin{proofsketch}
By (1) and (3), it should hold that (5) $v_2 \in \relv {k_2}
{\Gamma_{12}} {s_{12}} {S}$.  Since (2) holds, it should also hold
that ${t_i} \in \rele {\min(k_1,k_2)} {\Gamma_{12} \envplus{{x_i} :
    S}} {s_{12}} T$ by monotonicity of the logical relation on all
subscripts. Then, we can instantiate $x_i$ in the complete store to
map to what $v_2$ maps to. This should be fine by (5) and
monotonicity. Thus, ${t_i} \in \rele {\min(k_1,k_2)} {\Gamma_{12}
  \envplus{{x_i} : S}} {s_{12} \envplus{{x_i} \mapsto s_{12}(v)}}
T$. Thanks to (4), we don't actually need $x_i$ to be held abstract in
the environment, because it won't occur in $T$ or its expansion, so
we can use the actual type constructor of $v_2$, say $T_{v_2}$, instead
of $S$ for $x_i$: ${t_i} \in \rele {\min(k_1,k_2)} {\Gamma_{12}
  \envplus{{x_i} : {T_{v_2}}}} {s_{12} \envplus{{x_i} \mapsto
      s_{12}(v)}} T$. This implies what needs to be shown.

\end{proofsketch}
